Next Trippy Structures\thanks{Supported by organization x.}

### 2019-02-27 paper.tex
Use the old example for TTCTR

\subsection{\ttctr}
Version de spire y despues la variante nueva (\ctr).

@@

\subsection{Comparing \acumm and \ctr}
\label{sec:comp}
Better show this after they have been both explained... \marginpar{\tiny Include TTCTR in the table}

>>>>

\subsection{\ttctr}
The \ttctr was introduced in \cite{brisaboa2018new}.

Version de spire y despues la variante nueva (\ctr). \marginpar{\tiny Este ejemplo es complicado de editar, para un ejemplo sobre el nuevo ejemplo habria que hacer uno nuevo...}

\begin{figure}[tbhp]
	%\vspace{-0.2cm}
    \includegraphics[width=1.00\textwidth]{ttctr_daniil.eps}
	%\vspace{-0.3cm}
	\caption{Structures involved in the creation of a \ttctr}
	\label{fig:ttctr}
	%\vspace{-0.2cm}
\end{figure}

@@

\subsection{Comparing \acumm~and \ctr}
\label{sec:comp}
Better show this after they have been both explained... \marginpar{\tiny Include TTCTR in the table}
